---
title: "Into to R Tutorial"
author: "Sarah Narvaiz"
date: "2022-02-01"
tags: ["R tutorial"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First of all, happy February 1st! `r emo::ji("heart")`

The Spring 2022 semester just started and I get to serve as the teaching assistant for our Statistics 3 course. We will be using R and RStudio during this course to teach advanced statistical concepts and modeling. In this class we cover topics such as data cleaning, handling missing data, causal inference, multiple regression, mediation, and moderation. Given that many of the students who take this class have little to no exposure to R, we spend the first two weeks in class reviewing R and how it can be used for data cleaning and basic statistical applications. 

My advisor allowed me to teach the second half of the first class giving an introduction to R. After class, I decided to turn this lesson into a YouTube video as a resource for R novices that would like to get their feet wet. 

Enjoy! 

# Introduction to R Video

```{r, eval=TRUE, echo=FALSE}
blogdown::shortcode("youtube", "_RB5kVMThmA")

```

